Typing a linear \picalc

### 2020-03-15 paper/paper.tex
Some changes in nomenclature

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Typing a linear \picalc}
\author{Uma Zalakain}{University of Glasgow, Scotland}
       {u.zalakain.1@research.gla.ac.uk}{https://orcid.org/0000-0002-3268-9338}{}
\author{Ornela Dardha}{University of Glasgow, Scotland}
       {ornela.dardha@glasgow.ac.uk}{https://orcid.org/0000-0001-9927-7875}{}
\authorrunning{U. Zalakain and O. Dardha}
\Copyright{Uma Zalakain and Ornela Dardha}
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10003753.10003761.10003764</concept_id>
<concept_desc>Theory of computation~Process calculi</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[300]{Theory of computation~Process calculi}
\keywords{pi calculus, linear, types, concurrency}
\supplement{\url{https://github/umazalakain/typing-linear-pi}}
\acknowledgements{I want to thank \dots}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

@@

In the \lamcalc{} $\beta$-reduction operates on syntactically adjacent terms.
In the \picalc{} wowever, the syntax introduces unnecessary distinctions
(e.g. semantically parallel composition is defined modulo associativity and commutativity).
There are several ways around this, a structural congruence relation being one of the historical ones.
(Others include labeled transition systems and higher inductive types.)

@@

Structural congruence is a congruent equivalence relation ship.
As such, rewrites can happen at any point in a process' recursive definition, and they are closed under reflexivity, symmetry and transitivity as shown in Figure \ref{struct-cong}.
In \S \ref{subject-congruence} we will prove that if two processes $P$ and $Q$ are structurally congruent and $P$ is well-typed, then $Q$ is well-typed.
Specifically, in the case of transitivity we must prove that if $P$ is structurally congruent with $Q$ and $Q$ with $R$, and $P$ is well-typed, then so is $R$.
To do so, we will have to proceed by induction and first get a proof of the well-typedness of $Q$, then use that to reach $R$.
To show that the doubly recursive call terminates we index the equivalence relation $=$ by the type $\Rec$, which models the structure of the recursion.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Typing a linear \picalc}
\author{Uma Zalakain}{University of Glasgow, Scotland}
       {u.zalakain.1@research.gla.ac.uk}{https://orcid.org/0000-0002-3268-9338}{}
\author{Ornela Dardha}{University of Glasgow, Scotland}
       {ornela.dardha@glasgow.ac.uk}{https://orcid.org/0000-0001-9927-7875}{}
\authorrunning{U. Zalakain and O. Dardha}
\Copyright{Uma Zalakain and Ornela Dardha}
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10003753.10003761.10003764</concept_id>
<concept_desc>Theory of computation~Process calculi</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[300]{Theory of computation~Process calculi}
\keywords{pi calculus, linear, types, concurrency}
\supplement{\url{https://github/umazalakain/typing-linear-pi}}
\acknowledgements{We want to thank Wen Kokke, James Wood, Guillaume Allais, Bob Atkey, and Conor McBride for their thoughts, patience, work, education and camaraderie.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We live in a concurrent world where any given state is often decided by the interaction between a myriad of parties --- people, machines, processors, services, networks.
As humans, we aim to model, predict, and even construct such interactive systems.
As mathematicians, abstraction is our tool of choice to do so.

@@

The properties guaranteed by the picalc

@@

In the \lamcalc{} $\beta$-reduction operates on syntactically adjacent terms.
In the \picalc{} however, the syntax introduces unnecessary distinctions
(e.g. semantically parallel composition is defined modulo associativity and commutativity).
There are several ways around this, a structural congruence relation being one of the historical ones.
(Others include labeled transition systems and higher inductive types.)

@@

Structural congruence is a congruent equivalence relation.
As such, rewrites can happen at any point in a process' recursive definition, and they are closed under reflexivity, symmetry and transitivity as shown in Figure \ref{struct-cong}.
In \S \ref{subject-congruence} we will prove that if two processes $P$ and $Q$ are structurally congruent and $P$ is well-typed, then $Q$ is well-typed.
Specifically, in the case of transitivity we must prove that if $P$ is structurally congruent with $Q$ and $Q$ with $R$, and $P$ is well-typed, then so is $R$.
To do so, we will have to proceed by induction and first get a proof of the well-typedness of $Q$, then use that to reach $R$.
To show that the doubly recursive call terminates we index the equivalence relation $=$ by the type $\Rec$, which models the structure of the recursion.
